### 2018-10-01 Manuscript/Manuscript.tex
minor updates

\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{Park et al., in preparation for XXX}
\rhead{\thepage}

@@

\begin{flushleft}
{\Large \textbf{XXX}}
\\
Yuem Park\textsuperscript{1},
Nicholas L. Swanson-Hysell\textsuperscript{1}
\\
\bigskip
\textsuperscript{1} Department of Earth and Planetary Science, University of California, Berkeley, CA, USA
\\
\textsuperscript{2} XXX
\bigskip

@@

\noindent\textit{This article is in preparation for submission to XXX.}

>>>>

\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{Park et al., in preparation for AGU book entitled \textit{Environmental Change and Large Igneous Provinces}}
\rhead{\thepage}

@@

\begin{flushleft}
{\Large \textbf{XXX}}
\\
Yuem Park\textsuperscript{1},
Nicholas L. Swanson-Hysell\textsuperscript{1},
Francis A. Macdonald\textsuperscript{2}
Lorraine E. Lisiecki\textsuperscript{2}
\\
\bigskip
\textsuperscript{1} Department of Earth and Planetary Science, University of California, Berkeley, CA, USA
\\
\textsuperscript{2} Department of Earth Science, University of California, Santa Barbara, CA, USA
\bigskip

@@

\noindent\textit{This article is in preparation for submission to \textit{Environmental Change and Large Igneous Provinces}.}
